\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Chen Su}
\address{Shanghai, CN}
\address{\href{mailto:ghosind@gmail.com}{ghosind@gmail.com} \\ \href{https://ghosind.com}{ghosind.com} \\ \href{github.com/ghosind}{github.com/ghosind}}

\begin{document}

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

  {\bf B.Eng. in Computer Science and Technology} \hfill {Jane 2017}

\end{rSection}

%----------------------------------------------------------------------------------------
% TECHNICAL STRENGTHS
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}
  \begin{itemize}
    \itemsep -3pt {}
    \item Strong knowledge of C, Golang, Javascript/Typescript, and C\# software development.
    \item Design and implement scalable, highly available services with Docker and Kubernetes.
    \item Knowledge of database schema design, and SQL, experience in MySQL, MongoDB, and ElasticSearch.
    \item Proficient in UNIX/Linux environment, and shell scripting.
    \item Familiar with AWS and AliCloud services.
    \item Excellent git version management skills.
    \item Knowledge of Web development with HTML5, Node.js, and React.
    \item Ability to find out security and reliability issues.
    \item Strong Chinese communication skills, and able to working with international teams.
    \item Contributed to open source projects: thinkjs, upterm, etc.
  \end{itemize}
\end{rSection}


%----------------------------------------------------------------------------------------
% PROJECTS
%----------------------------------------------------------------------------------------
\begin{rSection}{PROJECTS}
\vspace{-1.25em}

\item \textbf{FatCoupon} {Node.js, Golang, MongoDB, AWS} \hfill \href{www.fatcoupon.com}{fatcoupon.com}
\begin{itemize}
  \itemsep -3pt {}
  \item Develop a Node.js monolithic service, Golang micro-services, and AWS Lambda serverless functions.
  \item Support over 10 million requests per day (over 100 requests per second) by 9 docker instances (3x 2c4g EC2 instance, with 20\% CPU baseline).
  \item Store data in MySQL and MongoDB to improve performance, and cache data by Redis.
  \item Collect and analysis data from various sources.
  \item Provide fuzzing text search by ElasticSearch.
\end{itemize}

\item \textbf{FTC Short Link} {Golang, MySQL, AWS} \hfill \href{ftc.cash}{ftc.cash}
\begin{itemize}
  \itemsep -3pt {}
  \item Allocate unique id for every unique link by MySQL, and filter duplicate link by hashing functions.
  \item Liner transformation a link id to pseudorandom number by linear congruential generator algorithm (LCG), and encode it by Base62 algorithm.
  \item Deploy service to AWS Lambda to provide high availability and global acceleration.
\end{itemize}

\item \textbf{DVM} {ShellScript} \hfill \href{github.com/ghosind/dvm}{github.com/ghosind/dvm}
\begin{itemize}
  \itemsep -3pt {}
  \item Create an NVM-like Deno version manager project with Shellscript.
  \item Design, develop, and maintain the open source project as the core developer and maintainer.
  \item Create test cases and GitHub Actions automation testing flow.
  \item The project has been recommended by Gitee official team.
\end{itemize}

\end{rSection}


%----------------------------------------------------------------------------------------
% WORK EXPERIENCE
%----------------------------------------------------------------------------------------
\begin{rSection}{EXPERIENCE}

\textbf{Backend Engineer} \hfill May 2019 - Present\\
FatCoupon \hfill \textit{}
\begin{itemize}
  \itemsep -3pt {}
  \item Develop backend service to provide Restful API for web and mobile applications.
  \item Design and develop micro-service architecture, and supporting inter-services communication by HTTP, gRPC, and MQ.
  \item Design database schema (including MySQL and MongoDB), and optimize query performance.
  \item Design scalable services with Docker, Kubernetes, and AWS Lambda.
  \item Create Shellscript and Makefile scripts to automate the development and deployment processes.
  \item Modify CDN pipeline to provide custom resizing and caching third-party resources.
  \item AWS services and Linux OS management.
  \item Create documentation with Swagger and markdown files.
\end{itemize}

\textbf{Backend Engineer} \hfill Aug 2018 - Feb 2019\\
Timepop \hfill \textit{}
\begin{itemize}
  \itemsep -3pt {}
  \item Develop a Node.js service to provide GraphQL API for mobile applications.
  \item Implement recommendation system by FtF algorithm.
  \item Develop instant chatting system based on Websocket.
  \item Assist frontend team with developing mobile application with React Native framework.
\end{itemize}

\textbf{Backend Engineer} \hfill Apr 2018 - Aug 2018\\
Dianda \hfill \textit{}
\begin{itemize}
  \itemsep -3pt {}
  \item Lead 5 engineer teams to develop B2B products, including both Node.js services and web pages.
  \item Participate in the product prototype design with PM and sales department.
  \item Refactor and optimize the existing code, migrate Node.js 0.10 projects to Node.js 8.
  \item Mentor junior engineers and interns.
  \item Review code and fix bugs.
\end{itemize}

\textbf{Development Engineer} \hfill May 2017 - Nov 2017\\
Pinming Software \hfill \textit{}
\begin{itemize}
  \itemsep -3pt {}
  \item Develop building information management software based on C\#/C++ and Revit SDK.
  \item Develop Windows desktop software by WPF framework.
  \item Recognize and convert CAD file to 3D models.
  \item Import and export data from 3D models to SQLite database.
\end{itemize}

\end{rSection}

\end{document}
